Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-05-30 analysis/paper/supplement/supplement.Rmd
More explanation of grade penalty and simple cost methods
re-run results

## Grade penalty and simple cost functions

@@

We compared the speed and peak RAM usage of the MST and ILCP methods with landings regularly sampled at 10 per km^2^ (high density) or using only the cutblock centroids as landings on weight rasters of three different resolutions (1000 m, 500 m and 100 m), giving 18 297, 72 633 and 1 815 825 nodes in the cost graph, respectively. Each cell in the raster becomes a node in the graph used to determine the shortest path which increases the time and memory requirements of the projection. Benchmarking was done using Azure Standard A4 v2 nodes which have 4 cores and 8 GB of RAM, chosen to match a typical laptop. Each projection was run on a separate node and the `peakRAM` package was used to measure the total time to run the projection and the maximum memory used at any point in the analysis [@quinn_peakram_2024]. We also timed the execution of the Hardy QGIS plugin with the 100 m resolution weights raster.

>>>>

## Grade penalty and simple cost methods for setting edge weights

@@

We compared the speed and peak RAM usage of the MST and ILCP methods with landings regularly sampled at 10 per km^2^ (high density) or using only the cutblock centroids as landings on weight rasters of 3 different resolutions (1000 m, 500 m, 100 m, 30 m and 10m), giving 18 297, 72 633, and 1 815 825nodes in the cost graph, respectively. We also attempted to include resolutions of 30 m and 10 m (23 787 140 and 214 072 800 nodes, respectively) but these crashed due to insufficient memory. Each cell in the raster becomes a node in the graph used to determine the shortest path which increases the time and memory requirements of the projection. Benchmarking was done using Azure Standard A4 v2 nodes which have 4 cores and 8 GB of RAM, chosen to match a typical laptop. Each projection was run on a separate node and the `peakRAM` package was used to measure the total time to run the projection and the maximum memory used at any point in the analysis [@quinn_peakram_2024]. We also timed the execution of the Hardy QGIS plugin with the 100 m resolution weights raster.
